### 2018-09-17 scripts/04-method_testing/README.Rmd
update readmes with github_markdown_nested format
update readmes to nested github document
update method testing scripts readme

---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Method testing

Here, we test the methods on some small real and toy datasets, to capture errors early on and make sure all methods run fine on these "simple" datasets.

These testing results are in the end pushed to [https://dynverse.github.io/dynmethods_automated_testing/index.html](https://dynverse.github.io/dynmethods_automated_testing/index.html)

>>>>

---
output: dynbenchmark::github_markdown_nested
---

# Method testing

Each method is tested on a few small real and toy datasets. Ideally, each method should be able to execute successfully on each of these datasets.
If a method is not able to infer a trajectory on any of the datasets, it will not be included in any of the next experiments.

Overview experiment:
```{r}
dynbenchmark::render_scripts_documentation()
```
